{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-07 Paper/main.tex
Shortened Introduction

	Functional Data Analysis (FDA), which has its roots in the work of Ulf Grenander and Kari Karhunen, is gaining more attention as researchers from different fields collect data that is functional in nature. Although classical statistical methods can often process this data, FDA has advantages in that it allows extracting information given by properties such as the smoothness of the underlying process or its derivatives (cf. \cite{levitin_introduction_2007}).	As \cite{kokoszka_introduction_2017} describe, using methods from FDA should be considered when one variable of a given data set can be seen as smooth curves or functions.	 
	Therefore, data sets in FDA can include both realizations of scalar random variables and realizations of random functions. Examples of such curves are the absorption curves of light in the Near-infrared (NIR) spectrum by chemical samples, an example which will be used in later parts of this paper.\footnote{For more details on Near-Infrared-Spectroscopy, refer to the section on Near-Infrared-Spectroscopy in the Appendix.}  
	This paper introduces Functional Linear Regression in a scalar-on-function setting relating functional predictors to a scalar response as described by Equation \ref{DGP1}.

	 \begin{equation}\label{DGP1}
	 	Y(\omega) = \alpha + \int_{0}^{1}{X(\omega)(s)\beta(s) \mathrm{d}s} + \epsilon(\omega),
	 	\qquad i = 1, ..., N
	 \end{equation}

	Here, $X(\omega)$ is a random function, $Y(\omega)$ is a scalar response variable and $\beta(t)$ is a coefficient function. The distinct feature of this framework is that the regressor is a function, which makes a different approach to estimation necessary because the problem of estimating $\beta(t)$ is inherently infinite-dimensional. This paper then introduces two distinct ways of estimating $\beta(t)$ using approximations dependent on a parameter choice and explores the selection of these parameters using cross validation.\\

	In Section \ref{Theory}, after introducing the necessary theoretical concepts, we describe two methods of estimating a scalar coefficient function using using the concepts of basis expansion and functional principal component analysis. Section \ref{Simulation} contains a description of structure and results of a Monte-Carlo Simulation aimed at choosing an appropriate functional basis and truncation parameter for the aforementioned methods. The application in Section \ref{Application} then uses the insights from theory and simulation to choose an appropriate basis for the estimation of Octane values of gasoline samples based on Near-Infrared absorption curves. In Section \ref{Outlook} we then give an outlook on possible extensions for this paper and describe limitations of our approach.

>>>>

	Functional Data Analysis (FDA), which has its roots in the work of Ulf Grenander and Kari Karhunen, is gaining more attention as researchers from different fields collect data that is functional in nature. Although classical statistical methods can often process this data, FDA has advantages in that it allows extracting information given by properties such as the smoothness of the underlying process or its derivatives (cf. \cite{levitin_introduction_2007}).	As \cite{kokoszka_introduction_2017} describe, using methods from FDA should be considered when one variable of a given data set can be seen as smooth curves or functions.	 
	Therefore, data sets in FDA can include both realizations of scalar random variables and realizations of random functions. Examples of such curves are the absorption curves of light in the Near-infrared (NIR) spectrum by chemical samples.\footnote{For more details on Near-Infrared-Spectroscopy, refer to the section on Near-Infrared-Spectroscopy in the Appendix.}

	This paper introduces Functional Linear Regression in a scalar-on-function setting. The distinct feature of this framework is that the regressor is a function, which makes a different approach to estimation necessary because the problem of estimating an unknown coefficient function is inherently infinite-dimensional. 
	We then introduce two distinct ways of translating this infinite-dimensional problem into a finite-dimensional problem that can addressed using theory from multivariate regression. First, a so-called basis expansion of the coefficient function and second, functional principal component regression. Both of these methods are dependent on a parameter choice called a truncation parameter for a functional basis and this paper focuses on exploring the selection of these parameters using cross validation.\\

	In Section \ref{Theory}, we introduce the necessary theoretical concepts, describe the estimation procedures and address the theoretical importance of the truncation parameter. Section \ref{Simulation} contains a description of structure and results of our Monte-Carlo Simulation which is aimed at choosing an appropriate functional basis and truncation parameter for the aforementioned methods. The application in Section \ref{Application} then uses the insights from theory and simulation to choose an appropriate basis for the estimation of Octane values of gasoline samples based on Near-Infrared absorption curves. In Section \ref{Outlook} we give an outlook on possible extensions for this paper and describe limitations of our approach.
